---
title: "vab"
author: "ken"
format: html
---

Vincent Arel-Bundock's list of datasets at <https://raw.githubusercontent.com/vincentarelbundock/Rdatasets/master/datasets.csv>, classified by me.


```{r}
library(tidyverse)
library(pingr)
my_url <- "https://raw.githubusercontent.com/vincentarelbundock/Rdatasets/master/datasets.csv"
datasets_all <- read_csv(my_url)
datasets_all
```

testing for online using idea at <https://stackoverflow.com/questions/5076593/how-to-determine-if-you-have-an-internet-connection-in-r>

```{r}
online <- is_online()
online
```

if online, re-download (might have been updated); if not (eg, on the bus), read from my store:

```{r}
if (online) {
  my_url <- "https://raw.githubusercontent.com/vincentarelbundock/Rdatasets/master/datasets.csv"
  datasets_all <- read_csv(my_url)
  datasets_all
  write_rds(datasets_all, "datasets_all.rds")
} else {
  datasets_all <- read_rds("datasets_all.rds")
}
datasets_all
```

are there any packages here that aren't in my list of datasets?

```{r}
datasets_all %>% count(Package) -> vab_packages
vab_packages
```

my datasets (run from all-datasets.Rmd, seems to run View to display)

```{r}
d %>% count(Package) -> my_packages
```

I want the packages that VAB has and I don't (first time)

```{r}
vab_packages %>% 
  anti_join(my_packages, join_by("Package")) %>% 
  pull(Package)
```

(61 the first time on 76)

```{r}
library(COUNT)
```

check (the first time I got 23 packages)

do again

```{r}
vab_packages %>% 
  anti_join(my_packages, join_by("Package")) %>% 
  pull(Package)

```

and now I am complete.

Next, what packages do I have on desktop that are not on 76?


